<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{rmetadata vignette}
-->

Local setup of Solr and querying using solr R package, on Mac OSX
======

**A general purpose R interface to [Solr](http://lucene.apache.org/solr/)**

This package only deals with exracting data from a Solr endpoint, not writing data (pull request or holla if you're interested in writing solr data).

### Solr info

+ [Solr home page](http://lucene.apache.org/solr/)
+ [Highlighting help](http://wiki.apache.org/solr/HighlightingParameters)
+ [Faceting help](http://wiki.apache.org/solr/SimpleFacetParameters)
+ [Installing Solr on Mac using homebrew](http://ramlev.dk/blog/2012/06/02/install-apache-solr-on-your-mac/)
+ [Install and Setup SOLR in OSX, including running Solr](http://risnandar.wordpress.com/2013/09/08/how-to-install-and-setup-apache-lucene-solr-in-osx/)

### Quick start

**Install**

Install dependencies

```{r, eval=FALSE}
install.packages(c("rjson","plyr","httr","XML","assertthat"))
```

Install solr

```{r, eval=FALSE}
install.packages("devtools")
library(devtools)
install_github("ropensci/solr")
```

```{r}
library(solr)
```

**Define stuff** Your base url and a key (if needed). This example should work. You do need to pass a key to the Public Library of Science search API, but it apparently doesn't need to be a real one.

```{r}

```
